Manuscript Figures for Genome Biology

### 2018-05-28 manuscript_figures/manuscript_figures.Rmd
Add separate color scale to sim in Fig4

# not excluding any methods
Fig4All.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha, 
                               tableOnly = TRUE, excludeMethods = NULL)$method)
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL)
Fig4All

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                colorLow = "yellow", colorHigh = "navy",
                fill = "FDR",
                rowOrder = Fig4.rowOrder)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                rowOrder = Fig4.rowOrder)

>>>>

# not excluding any methods
Fig4All.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha, 
                               tableOnly = TRUE, excludeMethods = NULL)$method)
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL)
Fig4All
```

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4.rowOrder) +
          scale_fill_gradient2(high = scales::muted("red"), 
                         mid = "white", 
                         low = scales::muted("blue"), 
                         midpoint = alpha)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                colorLow = scales::muted("blue"), 
                colorHigh = "white",
                rowOrder = Fig4.rowOrder)
